High-Throughput-derived Biologically-Inspired Features for Unconstrained Face Recognition

### 2011-11-21 results.tex
Fix figure dimensions, and flesh out bib

\begin{figure*}[ht]
\centering
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.6]{figures/within_roc.pdf}
  \label{fig:within_rocs}
}
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.6]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}

@@

\begin{figure*}[ht!]
\centering
\subfigure[\small{V1-like}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_v1like_a_plus.pdf}
  \label{fig:nfaces_v1like}
}
\subfigure[\small{HT-L2-1st}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_ht1_1_l2_1st.pdf}
  \label{fig:nfaces_l2}
}
\subfigure[\small{HT-L3-1st}]{
  \includegraphics[scale=0.5]{figures/nfaces_variation_NaturalBg_ht1_1_l3_1st.pdf}
  \label{fig:nfaces_l3}
}
\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by model}}
\label{fig:nfaces_by_model}
\end{figure*}

>>>>

\begin{figure*}[ht]
\centering
\subfigure[\small{within-model-class blends}]{
  \includegraphics[scale=0.7]{figures/within_roc.pdf}
  \label{fig:within_rocs}
}
\subfigure[\small{across-model-class blends}]{
  \includegraphics[scale=0.7]{figures/mega_blend_roc.pdf}
  \label{fig:megablend_rocs}
}

@@

\begin{figure*}[ht!]
\centering
\subfigure[\small{V1-like}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation_NaturalBg_v1like_a_plus.pdf}
  \label{fig:nfaces_v1like}
}
\subfigure[\small{HT-L2-1st}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation_NaturalBg_ht1_1_l2_1st.pdf}
  \label{fig:nfaces_l2}
}
\subfigure[\small{HT-L3-1st}]{
  \includegraphics[scale=0.55]{figures/nfaces_variation_NaturalBg_ht1_1_l3_1st.pdf}
  \label{fig:nfaces_l3}
}
\caption[]{{\bf Effect of number of synthetic faces to be discriminated, sorted by model}}
\label{fig:nfaces_by_model}
\end{figure*}
